Organization

### 2023-07-27 Analysis/data_organize.qmd
update data_organize and re-generate exp  files

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,reactable)
options(dplyr.summarise.inform=FALSE)
d <- readRDS(here("data/dPrune-05-21-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered=TRUE, levels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))
d$tOrder <- factor(d$tOrder, levels=c("testFirst","trainFirst"),labels=c("Test First","Train First"))
d$bandOrder <- factor(d$catOrder,levels=c("orig","rev"),labels=c("Original","Reverse"))
d$fb <- factor(d$fb,levels=c("continuous","ordinal"),labels=c("Continuous","Ordinal"))

@@

  (vb %in% c("800-1000","1000-1200","1200-1400") & bandOrder=="Original") |
  (vb %in% c("100-300","350-550","600-800") & bandOrder=="Reverse") ~ "Trained",
  TRUE ~ NA_character_
))
d$bandType <- factor(d$bandType,levels=c("Trained","Extrapolation"))

d<- d %>% mutate(id=as.factor(d$id),fullCond=as.factor(fullCond)) %>% 
  select(-catOrder,-mode) %>% relocate(bandOrder,bandType,.after=fb)

@@

@@

```{r}
d %>% select_if(is.factor) %>% select(-sbjCode,-id) %>% map(levels)
```

@@

saveRDS(d,here("data/dAll_07_04_23.rds"))
saveRDS(e1,here("data/e1_07_04_23.rds"))
saveRDS(e2,here("data/e2_07_04_23.rds"))
saveRDS(e3,here("data/e3_07_04_23.rds"))
# save csv versions
d %>% write_csv(here("data/dAll_07_04_23.csv"))
e1 %>% write_csv(here("data/e1_07_04_23.csv"))
e2 %>% write_csv(here("data/e2_07_04_23.csv"))
e3 %>% write_csv(here("data/e3_07_04_23.csv"))
```

d %>%
  distinct(id, condit, fb, bandOrder, tOrder) %>%
  group_by(condit, fb, bandOrder, tOrder) %>%
  summarise(n = n()) %>%
  kable()
```

@@

>>>>

pacman::p_load(tidyverse,here,knitr,kableExtra,reactable)
options(dplyr.summarise.inform=FALSE)
d <- readRDS(here("data/dPrune-07-27-23.rds")) %>% ungroup()

@@

  (vb %in% c("800-1000","1000-1200","1200-1400") & bandOrder=="Original") |
  (vb %in% c("100-300","350-550","600-800") & bandOrder=="Reverse") ~ "Trained",
  TRUE ~ NA_character_
))

d$bandType <- factor(d$bandType,levels=c("Trained","Extrapolation"))
d<- d %>% relocate(bandOrder,bandType,.after=bandInt)

@@

date.append="07-27-23"

saveRDS(d,here(paste0("data/dAll_",date.append,".rds")))
saveRDS(e1,here(paste0("data/e1_",date.append,".rds")))
saveRDS(e2,here(paste0("data/e2_",date.append,".rds")))
saveRDS(e3,here(paste0("data/e3_",date.append,".rds")))

# save csv versions
#d %>% write_csv(here(paste0("data/dAll_",date.append,".csv")))
# e1 %>% write_csv(here(paste0("data/e1_",date.append,".csv")))
# e2 %>% write_csv(here(paste0("data/e2_",date.append,".csv")))
# e3 %>% write_csv(here(paste0("data/e3_",date.append,".csv")))

@@

d %>% select_if(is.factor) %>% select(-sbjCode,-id) %>% map(levels)
d %>% select_if(is.factor) %>% select(-sbjCode,-id) %>% droplevels %>% map(levels)

@@

```{r}
d %>%
  distinct(id, condit, fb, bandOrder, tOrder) %>%
  group_by(condit, fb, bandOrder, tOrder) %>%
  summarise(n = n()) %>%
  kable()
```

@@

```{r}
d %>% filter(nGoodTrial==1,nTotal>100) %>% ggplot(aes(nTotal)) + geom_histogram() + facet_wrap(~condit)
d %>% filter(nGoodTrial==1,nTotal>100) %>% ggplot(aes(nTestNf)) + geom_histogram() + facet_wrap(~condit)
d %>% filter(nGoodTrial==1,nTotal>100) %>% ggplot(aes(nTrain)) + geom_histogram() + facet_wrap(~condit)
